Cooperative Decision Making for Communities of Autonomous Web Services

### 2013-12-14 proposal/presentation/ekpresentation/ehsan_presentation.tex
changes

\begin{frame}{Scenario Two: Web Services and Many Community}
    \begin{itemize}        
        \item Based on Coalition Structure theory
        \begin{itemize}    
            \item What coalitions to form? 
            \item Stability in coalition structure, is a partition of players, where no other partition can provide all agents with better utility.
        \end{itemize}
        \item Has to be distributed not centralized
        \item Merge and Split Algorithm
        \begin{itemize}
            \item Iterative
            \item Converges to a final partition
        \end{itemize}
    \end{itemize}
    \begin{figure}[htbp]
        \centering
        %\includegraphics[width=12cm, height=8cm]{figures/figure1.eps}
        \includegraphics[width=0.5 \columnwidth]{figures/scenario2.png}
        %%\includegraphics[scale=0.5]{figure1}
        %\caption{The NetBill payment protocol} \label{figure7}
    \end{figure}       	
\end{frame}

@@

>>>>

\begin{frame}{Scenario Two: Web Services and Many Communities}
    \begin{itemize}
        \item Based on Coalition Structure theory
        \begin{itemize}
            \item What coalitions to form?
            \item Stability in coalition structure, is a partition of players, where no other partition can provide all agents with better utility.
        \end{itemize}
        \item Has to be distributed not centralized
        \item Merge and Split Algorithm
        \begin{itemize}
            \item Iterative
            \item Converges to a final partition
        \end{itemize}
    \end{itemize}
    \begin{figure}[htbp]
        \centering
        %\includegraphics[width=12cm, height=8cm]{figures/figure1.eps}
        \includegraphics[width=0.5 \columnwidth]{figures/scenario2.png}
        %%\includegraphics[scale=0.5]{figure1}
        %\caption{The NetBill payment protocol} \label{figure7}
    \end{figure}       	
\end{frame}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{Induced subgraph games}

    \begin{table}
        \small
        \begin{tabular}{l|c|c|c|c}
        Representations                  & Space    & Shapley                  & Core Existence  & Complete     \\ \hline
        Graph (w+)                       & P        & P                        & P               & Not          \\
        Graph                            & P        & NP-Complete              & NP-Complete     & Not          \\
        Synergy                          & NA       & P (l input)              & P               & Not          \\
        Multi-issue                      & NA       & P (l input)              & NP-Complete     & Complete     \\
        MC-net                           & NA       & P (l input)              & NP-hard         & Complete     \\
        \end{tabular}
    \end{table}

    \begin{itemize}
        \item Our web service community valuation function representation ($v(C) = out(C)$) space requirement, grows linearly to input size.        
    \end{itemize}
